experiment 1

### 2021-11-13 experiments/9_strains/9_strains.Rmd
reorganisation, and added different number of strains

---
title: "6 strains"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

num_CB_strains <- 6
num_SB_strains <- 6
num_PB_strains <- 6

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/6_strains/data/sim_res_novar1.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/6_strains/data/sim_res_novar1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/6_strains/data/sim_res_highvar1.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/6_strains/data/sim_res_highvar1.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/6_strains/data/sim_res_novar2.RDS"))
```

```{r}
sim_res_novar2 <- readRDS(here("experiments/6_strains/data/sim_res_novar2.RDS"))
plot_dynamics(sim_res_novar2)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/6_strains/data/sim_res_highvar2.RDS"))
```

```{r}
sim_res_highvar2 <- readRDS(here("experiments/6_strains/data/sim_res_highvar2.RDS"))
plot_dynamics(sim_res_highvar2)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/6_strains/data/sim_res_novar3.RDS"))
```

```{r}
sim_res_novar3 <- readRDS(here("experiments/6_strains/data/sim_res_novar3.RDS"))
plot_dynamics(sim_res_novar3)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/6_strains/data/sim_res_highvar3.RDS"))
```

```{r}
sim_res_highvar3 <- readRDS(here("experiments/6_strains/data/sim_res_highvar3.RDS"))
plot_dynamics(sim_res_highvar3)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS"))

>>>>

---
title: "9 strains"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/9_strains/data/sim_res_novar1.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/9_strains/data/sim_res_novar1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/9_strains/data/sim_res_highvar1.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/9_strains/data/sim_res_highvar1.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/9_strains/data/sim_res_novar2.RDS"))
```

```{r}
sim_res_novar2 <- readRDS(here("experiments/9_strains/data/sim_res_novar2.RDS"))
plot_dynamics(sim_res_novar2)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/9_strains/data/sim_res_highvar2.RDS"))
```

```{r}
sim_res_highvar2 <- readRDS(here("experiments/9_strains/data/sim_res_highvar2.RDS"))
plot_dynamics(sim_res_highvar2)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/9_strains/data/sim_res_novar3.RDS"))
```

```{r}
sim_res_novar3 <- readRDS(here("experiments/9_strains/data/sim_res_novar3.RDS"))
plot_dynamics(sim_res_novar3)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt$pars[[medium_diverity_varexp_row]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/9_strains/data/sim_res_highvar3.RDS"))
```

```{r}
sim_res_highvar3 <- readRDS(here("experiments/9_strains/data/sim_res_highvar3.RDS"))
plot_dynamics(sim_res_highvar3)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

saveRDS(parameter, here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))

### 2021-11-13 experiments/checks_puzzles/checks_puzzles.Rmd
reorganisation, and added different number of strains

saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

### for testing

```{r eval = FALSE}
var_expt_small <- var_expt[c(no_diversity, medium_diverity_varexp_row),]
saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt_small, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))
run_ss_var_experiment(
  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial_small.RDS"))) %>%
saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
```

@@

```{r eval = FALSE}
## compare version 1 results to the current.
v1_ss_data <- readRDS(here("experiments/experiment 1/data/version1_ss_data_1e6_x2x6_factorial.RDS"))
v1_stab_data <- readRDS(here("experiments/experiment 1/data/version1_stab_data_1e6_x2x6_factorial.RDS"))

small_ss_data <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_small.RDS"))
small_stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial_small.RDS"))

xxxxx <- small_stab_data %>%
  select(-data, -pars, -ss_by_a_N_result, -ss_res, -sim_length) %>%
  filter(Species == "O")
v1_stab_data %>%
  filter(CB_var_gmax_s == 0, CB_var_h_s == 0,
         SB_var_gmax_s == 0, SB_var_h_s == 0,
         PB_var_gmax_s == 0, PB_var_h_s == 0) %>%
  filter(Species == "O")
v1_stab_data %>%
  slice(9620) %>%
  filter(Species == "O")
```

>>>>

saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@
